---
title: 'Notes for DataCamp: Sampling in R'
author: 'Author: YOUR NAME HERE'
date: '`r format(Sys.time(), "%A, %B %d, %Y @ %I:%M %p")`'
output: 
  html_document: 
    theme: yeti
    highlight: textmate
    toc: true
    toc_depth: 4
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, comment = NA)
```

***

### Modern Dive Chapter 8: Bootstrapping and Confidence Intervals

#### Course Description

Sampling is a cornerstone of inference statistics and hypothesis testing. It's tremendously important in survey analysis and experimental design. This course explains when and why sampling is important, teaches you how to perform common types of sampling, from simple random sampling to more complex methods like stratified and cluster sampling. Later, the course covers estimating population statistics, and quantifying uncertainty in your estimates by generating sampling distributions and bootstrap distributions. Throughout the course, you'll explore real-world datasets on coffee ratings, Spotify songs, and employee attrition.

#### Course Link

Go to [Sampling in R](https://learn.datacamp.com/courses/sampling-in-r).

### Packages Used

```{r}
library(tidyverse)
library(curl)
library(fst)
```

### Datasets Used

#### Spotify Song Data

Brief Description:

```{r}
tmp_file_1 <- tempfile()
fst_url_1 <- "https://assets.datacamp.com/production/repositories/5761/datasets/1496fc7387dda2feccc149d1add0d9617f83b215/spotify_2000_2020.fst"
curl_download(fst_url_1, tmp_file_1, mode = "wb")
spotify_population <- read_fst(tmp_file_1)
```

#### Employee Attrition

Brief Description:

```{r}
tmp_file_2 <- tempfile()
fst_url_2 <- "https://assets.datacamp.com/production/repositories/5761/datasets/af764828631d4a02b8a8184e9a2c207d8abb0087/attrition.fst"
curl_download(fst_url_2, tmp_file_2, mode = "wb")
attrition_pop <- read_fst(tmp_file_2)
```

#### Coffee Ratings 

Brief Description:

```{r}
tmp_file_3 <- tempfile()
fst_url_3 <- "https://assets.datacamp.com/production/repositories/5761/datasets/ed301a815089861bb77056f101c873dbbfdb5210/coffee_ratings_full.fst"
curl_download(fst_url_3, tmp_file_3, mode = "wb")
coffee_ratings <- read_fst(tmp_file_3)
```

### Bias Any Stretch of the Imagination

#### 


### Don't Get Theory Eyed

####


### The n's Justify the Means

####  


### Pull Your Data Up by Its Bootstraps

####


***
```{r}
sessionInfo()
```
