---
title: 'MDCH06 Multiple Regression Notes'
author: 'Author: YOUR NAME HERE'
date: '`r format(Sys.time(), "%A, %B %d, %Y @ %I:%M %p")`'
output: 
  html_document: 
    theme: yeti
    highlight: textmate
    toc: true
    toc_depth: 4
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, comment = NA)
```

***

### Packages

```{r}

```

### 6.1 One numerical and one categorical explanatory variable


#### 6.1.1 Exploratory data analysis


#### 6.1.2 Interaction model


#### 6.1.3 Parallel slopes model


#### 6.1.4 Observed/fitted values and residuals


### 6.2 Two numerical explanatory variables


#### 6.2.1 Exploratory data analysis


#### 6.2.2 Regression plane


#### 6.2.3 Observed/fitted values and residuals


### 6.3 Related topics


#### 6.3.1 Model selection


#### 6.3.2 Correlation coefficient


#### 6.3.3 Simpson’s Paradox


### 6.4 Conclusion


#### 6.4.1 Additional resources


#### 6.4.2 What’s to come?


### Learning Check

<p style="background-color:#9ED3AD; padding: 5px;">**Learning Check Questions**</p>

**(LC6.1)** (LC6.1) Compute the observed values, fitted values, and residuals not for the interaction model as we just did, but rather for the parallel slopes model we saved in `score_model_parallel_slopes`.


**(LC6.2)** Conduct a new exploratory data analysis with the same outcome variable $y$ `debt` but with `credit_rating` and `age` as the new explanatory variables $x_1$ and $x_2$. What can you say about the relationship between a credit card holder’s debt and their credit rating and age?


**(LC6.3)** Fit a new simple linear regression using `lm(debt ~ credit_rating + age, data = credit_ch6)` where `credit_rating` and `age` are the new numerical explanatory variables$x_1$ and $x_2$. Get information about the “best-fitting” regression plane from the regression table by applying the `get_regression_table()` function. How do the regression results match up with the results from your previous exploratory data analysis?


***
```{r}
sessionInfo()
```
